\plaintitle

### 2018-06-20 paper.tex
RC1 of the paper

\subsection{Testing in private (lab situation)}
% Belt (working prototype), Pinstripe, Usable Gestures, More Than Touch, SmartSleeve
Tests in a lab offer special possibilities. On one side the subject is not distracted by other stimuli and is more focused on the presented topic (in this case gesture testing). On the other side researchers can verify more data recorded by the sensor, receive voice feedback by the testing subject, which can include what and why they’re doing, the mental model behind the specific gesture, while they’re performing it.
The first prototype shown is ``Belt'' \cite{belt}, here users had a visual feedback for the belt-interaction, which was Google Glass. The main result, common to all interactions, is that the area reachable to the dominant hand is preferred. In the Belt case, in particular, the area which had a higher number of shortcuts is the front of the belt on the side of the dominant hand, where users expressed the easiness and comfortability of interacting with a body-worn device. The second case-study taken into account by this paper is ``Pinstripe'' \cite{pinstripe} in which test subjects would perform gestures in three different contexts, which are sitting, standing still and walking, and for each of them they’ll try to perform a grabbing gesture in all the sixteen areas of their body defined by the authors. For each of them they expressed the easiness and the personal acceptance of doing that gesture in that context. The most important discovery, found out also by the papers \cite{social-comfort, belt,more-touch}, is that the preferred part of the body is the upper side of the body, both for accessibility, which relates to easiness, and the comfort related to the social acceptance.
Moreover, as shown by \cite{more-touch} the mind model related to the touchscreen UI influences mostly the types of gestures (i.e. pinch to zoom is transferred from the Smartphone to the textile surface)

\subsection{Testing in public}
% Belt (no working tech), Usable Gestures, Pinstripe
%
When transferring from the private laboratory environment to the public and social environment where the subject meets people who are looking to himself, some different aspects can be noticed: first of all, the area, that was shown as acceptable is reduced considerably and comprehend only the arm, the pocket area and the sternum \cite{pinstripe}. This can be related to ``More than Touch’’  \cite{more-touch} were people felt uncomfortable in areas where they’re not used to perform touch gestures. An example that we can make is the fact that in the pocket area is normally reached to get the Smartphone, the wallet or the keys. In case of the forearm, instead, a person may look at his watch multiple times a day. One remark made in ``Pinstripe’’ \cite{pinstripe}, in fact, was that even though the sternum had a high rating. Female testers were underlying that it would not be socially acceptable to interact in that area, so the areas where the input should be placed depends on cultural background, sex and personal attitude.
When it comes to testing technology in public the most important factor is the observer. In the research done by Rico et. al. \cite{usable-gesture} one observation was, that not only the location played an important role, when it came to performing unusual gestures, but also the amount of observers and the degree of acquaintance. So in order to review a technology, which should be used in public situations, one has to test it in public situations to accurately define the degree of social acceptability.
“Because we observed differences between the first and second trials, we would recommend completing at least two trials when evaluating for social acceptability because users will develop preferences and change their acceptance rates after multiple trials. Additionally, we suggest that such trials be completed in real world settings, rather than lab ones.” \cite[p. 9]{usable-gesture}%([5] page 9)

@@

\subsection{Results}
\subsubsection{ Pinstripe} Focus on location - since the input method is inherently unobtrusive the input was not seen as problematic outside of suggestive regions (body map). Preferred regions: Pockets, not dominant arm.

\subsubsection{Usable Gestures}
Many reasons for social acceptability (location, observer (amount, acquaintance), type of gesture, position of wearable, type of wearable, etc.), in general natural gestures will always be more socially acceptable. Repetition can affirme user.

\subsubsection{The Social Comfort} When it comes to the placement of wearables there is a strong aversion to inappropriate body locations. While preferred positions are mainly chosen because easy accessibility, positions are mainly eluded to avoid embarrassment. Also the visual properties of a Wearable are an key factor for acceptance.
 \begin{figure*}[t]
   \includegraphics[width=\textwidth]{body-areas.png}
   \caption{Preferred Regions for Wearables in Different Studies Comparison \protect\cite{touch-wrist,pinstripe,social-comfort,belt,simpleskin}}
   \label{fig:body}
 \end{figure*}

 The single most prominent factor mentioned in the respective research projects, besides the type of gesture, was the body region where the Wearable was placed. The figure above shows the preferred regions in the individual studies. When comparing the researches there are two main observations to be made. First there is a strict aversion against socially suggestive regions for Wearables. These regions include genitalia, the bottom and, especially when asking female subjects, the upper torso area, including the sternum and collarbone.
 Second the all around preferred area for Wearable seems to be the forearm and wrist region - especially of the non dominant hand. \cite{touch-wrist,pinstripe,social-comfort,belt} %[1,6,7,8]
 This may be due to the fact that interaction with technologies on these body regions is already established and accepted in society through other devices such as watches and fitness bracelets. However, these body regions are also easy to reach and offer sufficient space for various gestures, which makes these body regions very suitable for body-worn controllers in the future as well.
\section{Outlook on social acceptability of wearables in the future}
Outlook on social acceptability of Wearables in the future

When looking into the future of Wearables one of the most interesting parts is the social acceptability. Since physical comfort, accessibility, and usability are for the most part figured out \cite{social-comfort}.
One, if not the most, important part of social acceptability are the performed gestures. Currently there is always a tradeoff which needs to be balanced when designing gestures, which are meant to be used in public situations. On one hand natural gestures are inherently more unobtrusive and socially acceptable. On the other hand these gestures are far more difficult to track and evaluate precisely, since they are easily confusable with everyday gestures that were not meant to be an input \cite{social-comfort}.
One approach to solve this problem is improving on better technology and tracking to avoid both confusing inputs and social discomfort at the same time. Another approach could be focussed around the social vocabulary more than around the gestures themselves.
``Because there does not currently exist a standard ‘vocabulary’ of gesture, it is correspondingly more difficult for viewers to match a perceived gesture with a previously-understood meaning.'' \cite[p. 4160]{social-comfort} %page 4160
Looking at this quote the other solution seems obvious. With the further adaptation of a novel technology there comes a better understanding of the gestures and finally a new social vocabulary regarding it. There were similar developments when the bluetooth headset \cite{social-comfort} or the Sony Walkman \cite{touch-wrist} was established.
In conclusion, the social acceptance of body-worn controllers can be increased through further developments and by bringing them more and more in contact with the public.

>>>>

\subsection{Testing in private (lab situation)}
% Belt (working prototype), Pinstripe, Usable Gestures, More Than Touch, SmartSleeve
Tests in a lab offer special possibilities. On one side the subject is not distracted by other stimuli and is more focused on the presented topic (in this case gesture testing). On the other side researchers can verify more data recorded by the sensor, receive voice feedback by the testing subject, which can include the narration of the task and the reasoning behind the execution.
The first prototype shown is ``Belt'' \cite{belt}, here users had a visual feedback for the belt-interaction, which was Google Glass. The main result, common to all interactions, is that the area reachable to the dominant hand is preferred. In the Belt case, in particular, the area which had a higher number of shortcuts is the front of the belt on the side of the dominant hand, where users expressed the easiness and comfortability of interacting with a body-worn device. The second case-study taken into account by this paper is ``Pinstripe'' \cite{pinstripe} in which test subjects would perform gestures in three different contexts, which are sitting, standing still and walking, and for each of them they’ll try to perform a grabbing gesture in all the sixteen areas of their body defined by the authors. For each of them they expressed the easiness and the personal acceptance of doing that gesture in that context. The most important discovery, found out also by the papers \cite{social-comfort, belt,more-touch}, is that the preferred part of the body is the upper side of the body, both for accessibility, which relates to easiness, and the comfort related to the social acceptance.
Moreover, as shown by \cite{more-touch} the mind model related to the touchscreen UI influences mostly the types of gestures (i.e. pinch to zoom is transferred from the Smartphone to the textile surface)

\subsection{Testing in public}
% Belt (no working tech), Usable Gestures, Pinstripe
%
When transferring from the private laboratory environment to the public and social environment where the subject meets people who are looking to himself, some different aspects can be noticed: first of all, the area, that was shown as acceptable is reduced considerably and includes only the arm, the pocket area and the sternum \cite{pinstripe}. This can be related to ``More than Touch’’  \cite{more-touch} were people felt uncomfortable in areas where they’re not used to perform touch gestures. An example that we can make is the fact that in the pocket area is normally accessed to get the Smartphone, the wallet or the keys. In case of the forearm, instead, a person may look at his watch multiple times a day. One remark made in ``Pinstripe’’ \cite{pinstripe}, in fact, was that even though the sternum had a high rating. Female testers were underlying that it would not be socially acceptable to interact in that area, so the areas where the input should be placed depends on cultural background, sex and personal attitude.
When it comes to testing technology in public the most important factor is the observer. In the research done by Rico et. al. \cite{usable-gesture} one observation was, that not only the location played an important role, when it came to performing unusual gestures, but also the amount of observers and the degree of acquaintance. So in order to review a technology, which should be used in public situations, one has to test it in public situations to accurately define the degree of social acceptability.
“Because we observed differences between the first and second trials, we would recommend completing at least two trials when evaluating for social acceptability because users will develop preferences and change their acceptance rates after multiple trials. Additionally, we suggest that such trials be completed in real world settings, rather than lab ones.” \cite[p. 9]{usable-gesture}%([5] page 9)

@@

\begin{figure*}[t]
  \includegraphics[width=\textwidth]{body-areas.png}
  \caption{Preferred Regions for Wearables in Different Studies Comparison
  \protect\cite{touch-wrist,pinstripe,social-comfort,belt,simpleskin}}
 \label{fig:body}
\end{figure*}

\subsection{Evaluation of placement areas for body-worn controllers }
The single most prominent factor mentioned in the respective research projects, besides the type of gesture, was the body region where the Wearable was placed. The figure above shows the preferred regions in the individual studies. When comparing the researches there are two main observations to be made. First there is a strict aversion against socially suggestive regions for Wearables. These regions include genitalia, the bottom and, especially when asking female subjects, the upper torso area, including the sternum and collarbone.
Second the all around preferred area for Wearable seems to be the forearm and wrist region - especially of the non dominant hand. \cite{touch-wrist,pinstripe,social-comfort,belt} %[1,6,7,8]
This may be due to the fact that interaction with technologies on these body regions is already established and accepted in society through other devices such as watches and fitness bracelets. However, these body regions are also easy to reach and offer sufficient space for various gestures, which makes these body regions very suitable for body-worn controllers in the future as well.
\section{Outlook on social acceptability of wearables in the future}
When looking into the future of Wearables one of the most interesting parts is the social acceptability. Since physical comfort, accessibility, and usability are for the most part figured out \cite{social-comfort}.
One, if not the most, important part of social acceptability are the performed gestures. Currently there is always a tradeoff which needs to be balanced when designing gestures, which are meant to be used in public situations. On one hand natural gestures are inherently more unobtrusive and socially acceptable. On the other hand these gestures are far more difficult to track and evaluate precisely, since they are easily confusable with everyday gestures that were not meant to be an input \cite{social-comfort}.
One approach to solve this problem is improving on better technology and tracking to avoid both confusing inputs and social discomfort at the same time. Another approach could be focussed around the social vocabulary more than around the gestures themselves.
``Because there does not currently exist a standard `vocabulary’ of gesture, it is correspondingly more difficult for viewers to match a perceived gesture with a previously-understood meaning.'' \cite[p. 4160]{social-comfort} %page 4160
Looking at this quote the other solution seems obvious. With the further adaptation of a novel technology there comes a better understanding of the gestures and finally a new social vocabulary regarding it. There were similar developments when the bluetooth headset \cite{social-comfort} or the Sony Walkman \cite{touch-wrist} was established.
In conclusion, the social acceptance of body-worn controllers can be increased through further developments and by bringing them more and more in contact with the public.
